{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-02-01 thesis/landslide.tex
start talking abt foundabug

\subsection{Scheduler}
\subsection{Memory analysis}
\subsection{Machine state manipulation}
\subsection{State space traversal}
% time travel, explore, arbiter
\subsection{Bug-finding output}
% symtable stuff goes here
% stack tracing goes here
% foundabug goes here
\sect{\ref{sec:landslide-bugreport}}

@@

\begin{itemize}
	\item {\tt mem\_check\_shared\_access()} ({\tt memory.c})
		will assert that kernel memory is direct-mapped.
	\item {\tt use\_after\_free()} ({\tt memory.c})
		will ignore use-after-free reads originating from kernel code during the {\tt swexn} system call
		(an extremely common and neither harmful nor technically interesting bug among student implementations).
	\item {\tt cause\_test()} ({\tt test.c})
		will issue keyboard input to type the test case name and press enter
		when the initialization sequence completes and the shell is blocked on {\tt readline}.
	\item {\tt kern\_mutex\_block\_others()} ({\tt schedule.c})
		will handle the special ``blocked on via mutex'' state changes
		whenever a mutex is acquired or released,
		for kernels which use the {\tt tell\_landslide\_kern\_mutex\_blocking()} annotation.
	\item {\tt sched\_update\_kern\_state\_machine()} ({\tt schedule.c})
		will handle the reference kernel's invocation of {\tt sched\_unblock()} within {\tt cond\_signal()}
		as a signal event for happens-before analysis.
	\item {\tt cause\_timer\_interrupt\_immediately()} ({\tt x86.c})
		will read the {\tt esp0} value out of the TSS to support user-to-kernel mode switches
		in timer interrupts injected during userspace execution.
\end{itemize}

>>>>

\subsection{Scheduler}
\subsection{Memory analysis}
\subsection{Machine state manipulation}
\subsection{State space traversal}
% time travel, explore, arbiter
\subsection{Bug-finding output}

\subsubsection{Symbol table}

The symbol table logic lives in {\tt symtable.c} and is pretty much a lot of glue code.
In the Simics version, Landslide relies on the {\tt deflsym} Simics object created by the 15-410 python scripts,
and queries its attributes using Simics API calls.
In the Bochs version, function names and line numbers are handled separately:
Bochs is patched with a new API function named {\tt bx\_dbg\_symbolic\_address\_landslide}%
\footnote{does the same thing as the existing {\tt bx\_dbg\_symbolic\_address}, but with a better type signature}
which provides function names and hexadecimal offsets;
while for line numbers, {\tt pebsim/pintos/build.sh}%
\footnote{Line numbers in Bochs for Pebbles/P2s are not supported yet; see {\tt p2-setup.sh} for the work-in-progress.}
generates a header file {\tt line\_numbers.h}
using {\tt objdump} and {\tt addr2line},
which the aforementioned hex offset then serves as an index into.

\subsubsection{Stack traces}

% features:
% noreturn functions, when last instr is a call, will avoid printing the next function in the binary
% various function eip offsets
% kernel to user mode swinches

\subsubsection{Preemption traces}

The preemption traces, described and exemplified in \sect{\ref{sec:landslide-bugreport}}, are generated by {\tt found\_a\_bug.c},
in cooperation with {\tt save.c}.
Whenever {\tt save.c} creates a preemption point, it captures a stack trace of the current thread at the point it was interrupted, and saves it in the preemption point tree.
{\tt found\_a\_bug.c} then traverses the current branch of the tree,
potentially producing both console output and HTML output (controlled by the {\tt HTML\_PRINTF} macro family).
It should be invoked by the {\tt FOUND\_A\_BUG} macro defined in {\tt found\_a\_bug.h},
or by {\tt FOUND\_A\_BUG\_HTML\_INFO}, which also allows the caller to specify a callback to print extra details (such as use-after-free stack traces) in the bug report.

@@

\begin{itemize}
	\item {\tt mem\_check\_shared\_access()} ({\tt memory.c})
		will assert that kernel memory is direct-mapped.
	\item {\tt use\_after\_free()} ({\tt memory.c})
		will ignore use-after-free reads originating from kernel code during the {\tt swexn} system call
		(an extremely common and neither harmful nor technically interesting bug among student implementations).
	\item {\tt cause\_test()} ({\tt test.c})
		will issue keyboard input to type the test case name and press enter
		when the initialization sequence completes and the shell is blocked on {\tt readline}.
	\item {\tt kern\_mutex\_block\_others()} ({\tt schedule.c})
		will handle the special ``blocked on via mutex'' state changes
		whenever a mutex is acquired or released,
		for kernels which use the {\tt tell\_landslide\_kern\_mutex\_blocking()} annotation.
	\item {\tt sched\_update\_kern\_state\_machine()} ({\tt schedule.c})
		will:
		\begin{itemize}
			\item handle the reference kernel's invocation of {\tt sched\_unblock()} within {\tt cond\_signal()}
				as a signal event for happens-before analysis.
			\item when a {\tt vanish}ing thread is about to delete its Simics symbol table object,
				save a ``pre-vanish'' stack trace,
				which {\tt splice\_pre\_vanish\_trace} ({\tt stack.c}) will then splice into any subsequent stack traces by that thread,
				so the user can see the userspace execution sequence preceding the {\tt vanish} invocation.
		\end{itemize}
	\item {\tt cause\_timer\_interrupt\_immediately()} ({\tt x86.c})
		will read the {\tt esp0} value out of the TSS to support user-to-kernel mode switches
		in timer interrupts injected during userspace execution.
\end{itemize}
